Fabric-Elasticity Relationships of Tibial Trabecular Bone are Similar in Osteogenesis Imperfecta and Healthy Individuals

### 2021-11-18 09_Article/01_Revision2_Reviewers/Response to Reviewers_00_bis.tex

Page 9, second column, Discussion, Lines 50-52
\begin{quote}
	The linear regression plot (Figure 5b) shows that when the stiffness term decreases to \Add{1 MPa (}10\textsuperscript{0}\Add{)} \Del{MPa} and lower, the linear regression tends to overestimate the stiffness.
\end{quote}

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.5\textwidth]
	{Pictures/02_GR_OI_LMM}
	\caption{Linear regression results for original OI group using the fixed effects of the linear mixed-effect model.}
	\label{CV_BVTV2}
\end{figure}

\newpage
\section{Clinical refocusing}
\RC Both reviewers were concerned about the fit of the manuscript content with the audience of Bone. While I agree that the Bone audience is accustomed to technical papers, please consider further refocusing to the clinical aspect. I would question where it is necessary to explicitly include equations 2 and 3 (page 4) since those are presumably outlined in the cited reference. If needed at all, considering moving to Appendix. Furthermore, equation 7 is not explained and therefore its relevance (and frequent reference later in the Discussion) is not clear.

\AR We understand your concern and agree to further refocusing to the clinical aspect. Regarding equations 2 and 3, even if they are outlined in cited references, we think that they are necessary for technical completeness. On the other hand, as they are more related to technical aspect we moved them in Appendix, as suggested. The text citing equation 7 was modified to describe the term contained and the signification of this NE, see below. Moreover, equations 1, 6, and 7 (for the fabric, the $R^2_{adj}$ and the norm error NE, respectively) were moved into Appendix A as well. We hope that these firsts steps will help to decrease the technical difficulty and increase the clarity of the paper from a clinical point of view.

Page 5, second column, Methods 2.5.3, last paragraph
\begin{quote}
	Linear regression on Zysset-Curnier model was assessed using the adjusted Pearson correlation coefficient squared ($R^2_{adj}$) and relative error between the orthotropic observed and the predicted tensor using norm of fourth-order tensors (NE)\Del{, see Equation 6 and 7}. \Add{This relative norm error allows to quantify the accuracy of the prediction. Details of the computation of these numbers are available in Appendix A.}
\end{quote}

### 2021-11-18 09_Article/01_Revision2_Reviewers/Simon_2021_Bone_Manuscript_Revised.tex
Finish Response to Reviewers and manuscript revision

	After ROI cleaning, i.e. deletion of bone material regions unconnected to the main structure, the morphological analysis of ROIs was performed using medtool (v4.5; Dr. Pahr Ingenieurs e.U., Pfaffst\"{a}tten, Austria). The morphological parameters analyzed were: BV/TV, structural model index (SMI), trabecular number (Tb.N.), trabecular thickness (Tb.Th.), trabecular separation (Tb.Sp.), and the standard deviation of the trabecular separation (Tb.Sp.SD). Moreover, ROI tissue mineral density (TMD) and fabric was evaluated. The fabric tensor $\mathbf{M}$ was computed using mean intercept length (MIL) method \cite{Moreno2014}. It is a positive-definite second-order tensor computed as shown below.

	where $m_i$ are the eigenvalues of $\mathbf{M}$ and $\mathbf{M}_i$ are the dyadic product of the corresponding eigenvectors $\mathbf{m}_i$ \cite{Cowin1985,Harrigan1985}. The fabric tensor is independent of BV/TV and normalised with $tr(\mathbf{M}) = 3$. The fabric eigenvalues allow to compute the degree of anisotropy (DA) of the ROI by dividing the highest eigenvalue by the lowest one. Figure \ref{01_FabricExample} shows an example of a typical ROI with the visualisation of its fabric tensor.\\

@@

	The linear regression was performed using the \textsc{statsmodels} package from \textsc{Python 3.6}. Linear regression quality for the TMD analysis was assessed using the Pearson correlation coefficient squared ($R^2$) and the standard error of the estimate (SE). Linear regression on Zysset-Curnier model was assessed using the adjusted Pearson correlation coefficient squared ($R^2_{adj}$) and relative error between the orthotropic observed and the predicted tensor using norm of fourth-order tensors (NE), see Equation \ref{Eq205} and \ref{Eq206}\Add{, respectively}.

	\Add{Where $\mathbb{S}_o$ and $\mathbb{S}_p$ are the observed and predicted stiffness tensors, respectively. This relative norm error allows to quantify the accuracy of the prediction.}

@@

	The Zysset-Curnier model \cite{Zysset1995} computes the fourth order stiffness tensor $\mathbb{S}$ using the BV/TV or $\rho$, fabric tensor $\mathbf{M}$, three elasticity parameters $\lambda_0$, $\lambda_0$', and $\mu_0$, and two exponents, $k$ and $l$, as shown in Equation \ref{Eq202}.

@@

>>>>

	After ROI cleaning, i.e. deletion of bone material regions unconnected to the main structure, the morphological analysis of ROIs was performed using medtool (v4.5; Dr. Pahr Ingenieurs e.U., Pfaffst\"{a}tten, Austria). The morphological parameters analyzed were: BV/TV, structural model index (SMI), trabecular number (Tb.N.), trabecular thickness (Tb.Th.), trabecular separation (Tb.Sp.), and the standard deviation of the trabecular separation (Tb.Sp.SD). Moreover, ROI tissue mineral density (TMD) and fabric was evaluated. The fabric tensor $\mathbf{M}$ was computed using mean intercept length (MIL) method \cite{Moreno2014}. \Del{It is a positive-definite second-order tensor computed as shown below.}\\

	\Del{where $m_i$ are the eigenvalues of $\mathbf{M}$ and $\mathbf{M}_i$ are the dyadic product of the corresponding eigenvectors $\mathbf{m}_i$ }\cite{Cowin1985,Harrigan1985}\Del{. The fabric tensor is independent of BV/TV and normalised with $tr(\mathbf{M}) = 3$.} The fabric eigenvalues allow to compute the degree of anisotropy (DA) of the ROI by dividing the highest eigenvalue by the lowest one. Figure \ref{01_FabricExample} shows an example of a typical ROI with the visualisation of its fabric tensor.\\

@@

	The linear regression was performed using the \textsc{statsmodels} package from \textsc{Python 3.6}. Linear regression quality for the TMD analysis was assessed using the Pearson correlation coefficient squared ($R^2$) and the standard error of the estimate (SE). Linear regression on Zysset-Curnier model was assessed using the adjusted Pearson correlation coefficient squared ($R^2_{adj}$) and relative error between the orthotropic observed and the predicted tensor using norm of fourth-order tensors (NE)\Del{, see Equation \ref{Eq205} and \ref{Eq206}}. \Add{This relative norm error allows to quantify the accuracy of the prediction. Details of the computation of these numbers are available in Appendix \ref{A0}.}

@@

	The Zysset-Curnier model \cite{Zysset1995} computes the fourth order stiffness tensor $\mathbb{S}$ using the BV/TV or $\rho$, fabric tensor $\mathbf{M}$, three elasticity parameters $\lambda_0$, $\lambda_0$', and $\mu_0$, and two exponents, $k$ and $l$, as shown in Equation \ref{Eq202}. The fabric tensor $\mathbf{M}$ is a positive-definite second-order tensor computed as shown below.

	Where $m_i$ are the eigenvalues of $\mathbf{M}$ and $\mathbf{M}_i$ are the dyadic product of the corresponding eigenvectors $\mathbf{m}_i$ \cite{Cowin1985,Harrigan1985}. The fabric tensor is independent of BV/TV and normalised with $tr(\mathbf{M}) = 3$. Then, it is used to compute the stiffness tensor.

@@

	Finally, after performing the linear regression, quality of the results is evaluated using the relative error of the norm of fourth-order tensors (NE) and the adjusted Pearson's correlation coefficient ($R^2_{adj}$). These coefficients are computed as follow:

	Where $\mathbb{S}_o$ and $\mathbb{S}_p$ are the observed and predicted stiffness tensors, respectively.
